Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

fen <- fen %>% filter(publication_year >= min.year & publication_year <= max.year)
kun <- kun %>% filter(publication_year >= min.year & publication_year <= max.year)
```

@@

```{r 201606krakow-fennica-topfemale, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=10}

theme_set(theme_bw(20))
dfs <- fen %>% filter(author_gender == "female")
p <- top_plot(dfs, "author", ntop = 20)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count")
p <- p + ggtitle("Top female authors (Fennica)")
p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
pf = p

@@

```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=9}
theme_set(theme_bw(25))
library(sorvi)
df = df.preprocessed
dfs <- df %>% group_by(publication_year) %>%
         summarize(paper.per.doc = mean(paper.consumption.km2, na.rm = T))
p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_year)) +
       geom_line() + geom_point() +
       xlab("Publication Year") + ylab("Paper per document")
p <- p + ggtitle("Average paper consumption per document")
print(p)
```

@@

>>>>

fen <- fen %>% filter(publication_year >= min.year & publication_year <= max.year)
kun <- kun %>% filter(publication_year >= min.year & publication_year <= max.year)
df0 = bind_rows(fen, kun)
df0$catalogue = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))
```

@@

```{r 201606krakow-fennica-topfemale, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=10}
theme_set(theme_bw(20))
dfs <- fen %>% filter(author_gender == "female")
p <- top_plot(dfs, "author", ntop = 20)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count")
p <- p + ggtitle("Top female authors (Fennica)")
p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
pf = p

@@

@@

## Miscellaneous figures to consider

```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=9}
theme_set(theme_bw(25))
library(sorvi)
df = df0
dfs <- df %>% group_by(publication_year) %>%
         summarize(paper.per.doc = mean(paper.consumption.km2, na.rm = T))
p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_year)) +
       geom_line() + geom_point() +
       xlab("Publication Year") + ylab("Paper per document")
p <- p + ggtitle("Average paper consumption per document")
print(p)
```
